---
title: "Tightly integrated human and machine intelligence within an active learning approach to cropland mapping"


author:  

- name: Lyndon D. Estes
  affilnum: '1'
  
# - name: Francisco Rodriguez-Sanchez 
#   affilnum: 3
#   email: f.rodriguez.sanc@gmail.com
  
affiliation:

- affilnum: 1
  affil: Graduate School of Geography, Clark University, 950 Main Street, Worcester, MA 01610 USA

#   
# - affilnum: 2
#   affil: Big Name University, Department of R, City, BN, 01020, USA
#   
# - affilnum: 3
#   affil: Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain
    
output:

  pdf_document:
    fig_caption: yes
    fig_width: 7
    fig_height: 7
    keep_tex: yes
    number_sections: no
    template: manuscript.latex
    includes:
      in_header: header.tex

  html_document: null
  
  word_document: null

documentclass: article
classoption: a4paper
capsize: normalsize
fontsize: 11pt
geometry: margin=1in
linenumbers: yes
spacing: doublespacing
footerdate: yes
abstract: no
bibliography: 
  - references.bib
  - knitcitations.bib
csl: ecology.csl

---


```{r setup, include=FALSE, cache=FALSE, message = FALSE}

library(knitr)
library(citr)

#opts_knit$set(root.dir=normalizePath('../'))

### Chunk options: see http://yihui.name/knitr/options/ ###

## Text results
opts_chunk$set(echo = TRUE, warning = TRUE, message = TRUE, include = TRUE)

## Code decoration
opts_chunk$set(tidy = TRUE, comment = NA, highlight = TRUE)

## Cache
opts_chunk$set(cache = 2, cache.path = "output/cache/")

## Plots
opts_chunk$set(fig.path = "output/figures/")


```


```{r knitcitations, echo=FALSE, cache = FALSE}
library(knitcitations)
cleanbib()   
cite_options(citation_format = "pandoc")
```


\singlespace

\vspace{2mm}\hrule

Write your abstract here.

\vspace{3mm}\hrule

*Keywords*: rmarkdown, reproducible science

\doublespace

\bleft


# Introduction

[@Esteslargeareaspatiallycontinuous2018]

- The problem in general 
    - Africa in particular
    - Types of analyses that depend on cropland maps
- Why cropland mapping is hard
    - 3 problems
        - The target itself and its spectral variability and the spectral variability of its background
            - Spectral and spatial resolution of sensors
            - Poses a challenge for classification algorithms, which want both high resolution to be smaller than characteristic field size, but temporal contrast also
    - Training data dependence issues
        - Also interact with image resolution issues
        - Increasingly rely on high amounts of training data
        - Human interpretation error (training data quality)
          - Temporal mismatch with classification feedstock (Lesiv paper)
          - Errors in interpreting these sources of imagery
- Review of who does what to solve the problem (probably integrated with problem statement) 
    - croplands.org
- Our approach that tries to solve these three problems
- Within a framework that tightly integrates tightly training data collection
- And handles large-scale computation
- Segmented boundaries
    
# Methods

- Imagery and image processing methods
- Sample grid
- The system
    - Crowdsourcing platform
          - Training and validation data
          - Accuracy assessment
    - Machine learning
          - Feature engineering
          - ML pipeline Apache Spark
    - Iteration cycle
    - Segmentation

# Results

- Image quality and density
- Labeling results/quality
- Impact of features on accuracy
- Accuracy scores by iteration
- Accuracy by label quality
- Segmentation results 
  - field size class distributions
  - Improvement of accuracy

# Discussion

- Left unquantified is how much training on base maps matters

# Acknowledgement


# References


<!-- ```{r write_citations, cache=FALSE, include=FALSE} -->
<!-- write.bibtex(file="knitcitations.bib") -->
<!-- ``` -->

<div id = "refs"></div>


\eleft

\clearpage


<!-- \listoftables -->


\newpage

<!-- ```{r Table1, results='asis', echo=FALSE, cache=FALSE} -->
<!-- kable(head(iris), caption = "A glimpse of the famous *Iris* dataset.") -->
<!-- ``` -->


\newpage

<!-- ```{r Table2, results='asis', echo=FALSE, cache=FALSE} -->
<!-- kable(mtcars[10:16, ], caption = "Now a subset of mtcars dataset.") -->
<!-- ``` -->


\clearpage

<!-- \listoffigures -->


\newpage

<!-- ```{r Fig1, echo=FALSE, fig.cap="Just my first figure with a very fantastic caption.", cache=FALSE} -->
<!-- x <- rnorm(100) -->
<!-- y <- jitter(x, 1000) -->
<!-- plot(x, y) -->
<!-- ``` -->

\newpage

\blandscape

<!-- ```{r Fig2, echo=FALSE, fig.cap="Second figure in landscape format.", cache=FALSE} -->
<!-- a <- sort(rnorm(100)) -->
<!-- b <- c(rep("Group Small", 35), rep("Group Big", 65)) -->
<!-- boxplot(a ~ b) -->
<!-- ``` -->

\elandscape

\clearpage



```{r sessioninfo, echo = FALSE, eval = FALSE}
# set eval = FALSE if you don't want this info (useful for reproducibility) to appear 
sessionInfo()
```

