
# Analyses and figures

## Ghana reference grids

### Datasets

```{r, eval=FALSE}
library(raster)
library(sf)
library(dplyr)
library(ggplot2)
library(purrr)
library(rmapaccuracy)

res <- 0.005
res_supergrid <- 1
num_supergrid <- res_supergrid / res

data_path <- file.path("/Users", unname(Sys.info()["user"]),
                       "Dropbox/projects/activelearning/mapper/spatial/data")
master_grid <- raster(file.path(data_path, "processed/master_grid.tif"))
africa <- st_read(file.path(data_path, "external/africa_noisl_gcs.sqlite")) %>% 
  st_sf(crs = 4326)
africa_cont <- africa %>% st_union %>% st_sf
ghana <- africa %>% filter(country == "Ghana") %>% select(GEOMETRY)

tiles <- st_read(file.path(data_path, "processed/ghana_tiles.geojson"))
degrees <- raster(file.path(data_path, "processed/africa_aois.tif"))
# tiles <- raster(file.path(data_path, "processed/africa_aois.tif"))
```

### Figure 2: Grid System

```{r, eval = FALSE}
ghana_aois <- tiles %>% pull(aoi) %>% unique
degrees <- rasterToPolygons(degrees) %>% st_as_sf %>% 
  rename(aoi = africa_aois) %>% st_sf(crs = 4326)

ind <- 26  # index of selected AOI for plotting (from ghana_aois)

xylims <- st_coordinates(ghana)
maprange <-  c(range(xylims[, 1]), range(xylims[, 2]))

p1 <- ggplot(africa) + geom_sf(fill = "gray97", color = "grey", size = 0.25) +
  geom_sf(data = ghana, fill = "grey85", col = "grey", size = 0.3) +
  geom_sf(data = degrees %>% filter(aoi %in% ghana_aois),
          fill = "transparent", size = 0.3) +
  geom_sf(data = degrees %>% filter(aoi == ghana_aois[ind]), fill = "gray70",
          size = 0.3) +
  coord_sf(xlim = maprange[1:2], ylim = maprange[3:4]) +
  theme_void()
p1

xylims <- degrees %>% filter(aoi %in% ghana_aois[c(ind:27, 31:32)]) %>%
  st_coordinates(.)
maprange <-  c(range(xylims[, 1]), range(xylims[, 2]))

tile_sel <- tiles %>% filter(aoi == ghana_aois[ind])  # selected tile
p2 <- ggplot(ghana) + geom_sf(fill = "grey85", col = "grey") +
  geom_sf(data = degrees, fill = "transparent", size = 0.3) +
  geom_sf(data = tile_sel, fill = "gray70", size = 0.3) +
  geom_sf(data = tile_sel %>% slice(1), fill = "red3", size = 0.3) +
  coord_sf(xlim = maprange[1:2], ylim = maprange[3:4]) +
  theme_void()
p2

gpols <- crop(master_grid, tile_sel[1, ]) %>% rasterToPolygons(.) %>%
  st_as_sf %>% st_sf(crs = 4326)
p3 <- ggplot(tile_sel %>% slice(c(1:2, 21:22))) +
  geom_sf(fill = "grey80", size = 0.3) +
  # geom_sf(data = super_cellsr %>% slice(ints[1]), fill = "grey60") +
  geom_sf(data = gpols, fill = "red3", size = 0.3) +
  theme_void()
p3

g <- cowplot::plot_grid(p1, p2, p3, nrow = 1, scale = c(1, 1, 0.7), 
                        labels = LETTERS[1:3], label_x = 0.05)
ggsave("manuscript/figures/figure2.png", width = 7, height = 3, 
       units = "in", dpi = 300)

```

## Climatology figure (supplemental)

Grab CHIRPs monthly data from `mapper`
```{r, eval = FALSE}
library(stars)
dir(file.path(data_path, "external/climatology/chirps"), full.names = TRUE) %>% 
  stack(.) %>% crop(., ghana) -> chirps
rftot <- calc(chirps, sum)
monthly_pct <- chirps / rftot * 100
names(monthly_pct) <- lubridate::month(1:12, label = TRUE)
monthly_pct <- setZ(monthly_pct, lubridate::month(1:12, label = TRUE))
monthly_pct_stars <- stars::st_as_stars(monthly_pct)

# plot(monthly_pct_stars, breaks = seq(0, 35), ) + 
#   geom_sf(data = ghana, fill = "transparent", size = 0.3)
p <- ggplot() + geom_stars(data = monthly_pct_stars) + 
  facet_wrap("band", nrow = 2) + 
  geom_sf(data = ghana, fill = "transparent", size = 0.3) +
  scale_fill_viridis_c(breaks = seq(0, 35, 5), "%", na.value = "grey90") +
  xlab("") + ylab("") + ggtitle("Percent of annual rainfall by month") + 
  theme(panel.background = element_rect(fill = NA), 
        axis.text = element_blank(), axis.ticks = element_blank()) 
ggsave("manuscript/figures/si_rainfall_pct.png", height = 4, width = 6, 
       units = "in", dpi = 300)
```

### Mapping AOIs
```{r, eval = FALSE}
prod_groupings1 <- list(c(1216, 1217, 1283, 1284), c(1218, 1285), c(1219, 1286),
                        c(1348, 1349), 1350, c(1351, 1352), c(1413, 1414), 1415,
                        c(1416, 1417), c(1477, 1478), 1479, c(1480, 1481), 
                        c(1539, 1540), 1541, c(1542, 1543), 1599:1602)
map(1:length(prod_groupings1), function(x) {
  ind <- prod_groupings1[[x]]
  tiles %>% filter(aoi %in% ind) %>% mutate(grp = x) %>% select(aoi, tile, grp)
}) %>% reduce(rbind) -> aois

aois <- aois %>% group_by(grp) %>% 
  summarize(aois = mean(grp)) %>% ungroup
aois <- aois %>% 
  mutate(area = st_area(.) %>% units::set_units("km2") %>% as.numeric) %>% 
  select(grp, aois, area)
mean(aois$area)
range(aois$area)

st_write(aois, dsn = "external/data/aois.geojson")
```

## Map reference selection
A random draw of cells within each map AOI, scaled proportionally from 120 to the total area of each cell.

```{r, eval = FALSE}
aois <- aois %>% mutate(nref = ceiling(area / max(area) * 120)) %>% 
  select(aois, area, nref)

# extract ids
ref_sites <- lapply(1:nrow(aois), function(x) {  # x <- 15
  print(x)
  cells <- extract(master_grid, aois[x, ])[[1]]
  return(cells[!is.na(cells)])
})
# length(which(is.na(cells)))

# sample then in proportion
set.seed(1)
ref_sites_sample <- lapply(1:length(ref_sites), function(x) {
  sn <- aois[x, ] %>% pull(nref)
  rsites <- ref_sites[[x]]
  sample(x = ref_sites[[x]], size = sn, replace = FALSE)
}) 

# and select cell coordinates from database
pw <- "bqouhegFpwiEnfD%p6HZ67JsN"
con <- DBI::dbConnect(RPostgreSQL::PostgreSQL(), 
                      host = "labeller1.crowdmapper.org", dbname = "Africa", 
                      user = "postgis", password = pw)

xys <- lapply(1:length(ref_sites_sample), function(x) {
  print(x)
  rsites <- ref_sites_sample[[x]]
  xy <- tbl(con, "master_grid") %>% filter(id %in% rsites) %>% 
    select(id, name, x, y) %>% collect()
})
DBI::dbDisconnect(con)

# convert to polygons
gcs <- unname(unlist(st_crs(ghana))[2])
xypolys <- lapply(1:length(xys), function(x) {
  print(x)
  polys <- point_to_gridpoly(data.table::data.table(xys[[x]]), 
                             w = 0.005 / 2, gcs, gcs)
  polys %>% mutate(aoi = x) %>% select(name, aoi)
})
ref_sites_polys <- reduce(xypolys, rbind)

# ggplot(aois) + geom_sf() + 
#   geom_sf(data = ref_sites_polys, aes(color = factor(aoi))) + theme_void()
st_write(ref_sites_polys, dsn = here::here("external/data/ref_samples.sqlite"),
         delete_layer = TRUE)


# select PlanetScope data
planet <- lapply(1:6, function(x) {  # x <- 1
  cid <- ref_sites_sample[[x]]
  con <- DBI::dbConnect(RPostgreSQL::PostgreSQL(), dbname = "Africa", 
                        host = paste0("labeller", x, ".crowdmapper.org"), 
                        user = "postgis", password = pw)
  pdata <- tbl(con, "scenes_data") %>% 
    filter(cell_id %in% cid) %>% 
    select(cell_id, url, season) %>% collect()
  DBI::dbDisconnect(con)
  pdata %>% arrange(season, cell_id) %>% mutate(aoi = x) %>% 
    rename(id = cell_id) %>% select(id, aoi, season, url)
})
pth <- here::here(paste0("external/data/aoi", x, ".csv"))
readr::write_csv(planet[[1]], path = pth)


```

Create starter reference polygons for AOIs. These are fixed size in random placement in each cell. These can be moved more easily to capture pure classes
```{r, eval=FALSE}
# read back in ref sample points and create three random points in each per AOI
ref_sites_polys <- st_read(here::here("external/data/ref_samples.sqlite"))
set.seed(1)
ref_start_pts <- lapply(1:16, function(x) {
  print(x)
  start_pts <- suppressMessages(
    ref_sites_polys %>% filter(aoi == x) %>% 
      st_sample(size = rep(3, nrow(.)), silent = TRUE)
  )
  start_pts <- st_intersection(st_sf(start_pts), ref_sites_polys)
  xy <- start_pts %>% st_coordinates %>% as_tibble() %>% setNames(c("x", "y"))
  start_pts <- bind_cols(start_pts %>% as_tibble, xy) %>% select(name, x, y) %>% 
    data.table::data.table()
})

# ref_sites_polys %>% slice(2) %>% st_geometry() %>% plot
# plot(ref_start_pts_aoi1, add = TRUE)

# pick up names via intersection and convert to x, y points for use with 
# point_to_grid_poly

# create polygons from starter points, add class fields, etc. 
gcs <- unname(unlist(st_crs(tiles)))[2]
w <- 0.0001433
strt_pol_aoi1 <- point_to_gridpoly(ref_start_pts[[1]], w = w, gcs, gcs) %>% 
  group_by(name) %>% mutate(rid = 1:n()) %>% ungroup %>% mutate(class = NA) %>% 
  select(name, rid, class)
# strt_pol_aoi16 <- point_to_gridpoly(ref_start_pts[[16]], w = w, gcs, gcs) %>% 
#   group_by(name) %>% mutate(rid = 1:n()) %>% ungroup %>% 
#   mutate(class = NA) %>% select(name, rid, class)
# ref_sites_polys %>% slice(1) %>% st_geometry %>% plot
# plot(start_pols_aoi1[1:3, ], add = TRUE)

# check areas
# start_pols_aoi1 %>% st_area %>% mean
# start_pols_aoi16 %>% st_area %>% mean

st_write(strt_pol_aoi1, 
         dsn = here::here("external/data/ref_polys_ao1.sqlite"))
```

Grab necessary imagery off of S3
```{r, eval=FALSE}
library(aws.s3)
planet_aoi1 <- readr::read_csv(here::here("external/data/aoi1.csv"))
dnames <- here::here("external/data/imagery", c("GS", "OS"))
for(i in dnames) if(!dir.exists(i)) dir.create(i)

os <- get_bucket_df(bucket = "activemapper", 
                    prefix = "planet/composite_sr_buf/OS")

# os %>% select(Key, Size) %>% mutate(Size = as.numeric(Size)) %>% 
#   filter(Key %in% gsub("s3://activemapper/", "", planet_aoi1$url)) %>% 
#   summarize(sum(Size)) / 1e+9

os_urls <- planet_aoi1 %>% filter(season == "OS") %>% distinct(url) %>% 
  unname %>% unlist
for(i in os_urls[-length(os_urls)]) {
# for(i in os_urls) {  
  cmd <- paste("aws s3 cp", i, file.path(dnames[2], basename(i)))
  system(cmd)
}
gs_urls <- planet_aoi1 %>% filter(season == "GS") %>% distinct(url) %>% 
  unname %>% unlist
for(i in gs_urls) {
  cmd <- paste("aws s3 cp", i, file.path(dnames[1], basename(i)))
  system(cmd)
}



os_tiles <- os %>% select(Key, Size, Bucket) %>% 
  mutate(Size = as.numeric(Size)) %>% 
  filter(Key %in% gsub("s3://activemapper/", "", planet_aoi1$url))
  # with(get_object(object = os$KeyKey, bucket = Bucket, 
  #                 file = file.path(dnames[2], basename(Key))))
get_object(object = os_tiles$Key[1], bucket = os_tiles$Bucket[1], 
                  file = file.path(dnames[2], basename(os_tiles$Key[1])))

```





## Figure 4: Average quality of image tiles

Placeholder for now, as using imagined image quality.

```{r, eval=FALSE}
# randomly select cells, as if those used to assess image quality
set.seed(1)
tiles_ss <- tiles %>% sample_n(100)

# set up dummy values of quality, using rainfall as example and regression with
# some random noise added
rftiles <- unlist(extract(rftot, tiles_ss))  # rainfall
tiles_ss <- tiles_ss %>% mutate(rf = rftiles) %>% select(aoi, tile, rf)
rflm <- coef(lm(c(8, 1) ~ range(tiles_ss$rf)))  # regression 1 to 8
qual_preds <- rflm[1] + rflm[2] * tiles_ss$rf  # predict
set.seed(7) 
qual_preds <- round(qual_preds *  # random noise
                      runif(length(qual_preds), min = 0.7, max = 1.3))
qual_preds <- ifelse(qual_preds > 5, 5, qual_preds)  # force to 5
tiles_ss <- tiles_ss %>% mutate(Quality = factor(qual_preds)) %>% 
  select(aoi, tile, rf, Quality)

# random assignment of 1-5 by rainfall
p1 <- ggplot(africa) + geom_sf(fill = "gray97", color = "grey", size = 0.25) +
  geom_sf(data = tiles, fill = "grey85", col = "grey", size = 0.3) +
  geom_sf(data = ghana, fill = "transparent", col = "grey", size = 0.3) +
  geom_sf(data = tiles_ss, 
          mapping = aes(fill = Quality, color = Quality)) +   
  scale_fill_brewer(palette = "RdBu") + scale_color_brewer(palette = "RdBu") + 
  coord_sf(xlim = maprange[1:2], ylim = maprange[3:4]) + 
  theme_void()
p2 <- ggplot(tiles_ss) + 
  geom_histogram(aes(x = Quality), bins = 5, stat = "count", col = "grey", 
                 fill = "blue") + 
  xlab("Quality of composite") + ylab("N tiles") + 
  cowplot::theme_cowplot(font_size = 12)
g <- cowplot::plot_grid(p1, p1, p2, p2, nrow = 2, scale = c(1, 1, 0.9), 
                        labels = LETTERS[1:4], label_x = 0.05)
ggsave("manuscript/figures/figure4.png", width = 5, height = 5, 
       units = "in", dpi = 300)
```

### Accuracy within blocks

Placeholder. Use imagined accuracy based on rainfall, using dummy approach as with Figure 3.  This will be replaced by metrics from tables for each instance. 
```{r, eval=FALSE}
rf <- aois %>% st_centroid %>% extract(rftot, .)
aois <- aois %>% mutate(rf = rf)

# Rainfall-accuracy relationship
rflm <- coef(lm(c(0.9, 0.75) ~ range(aois$rf)))  # 75-90%
set.seed(7) 
aois <- aois %>% 
  mutate(Accuracy = (rflm[1] + rflm[2] * rf) * 
           runif(n(), min = 0.95, max = 1.05) * 100)

# Users
rflm <- coef(lm(c(0.85, 0.75) ~ range(aois$rf)))  # 75-90%
set.seed(1) 
aois <- aois %>% 
  mutate(User = (rflm[1] + rflm[2] * rf) * 
           runif(n(), min = 0.95, max = 1.05) * 100)

# Producers
rflm <- coef(lm(c(0.9, 0.75) ~ range(aois$rf)))  # 75-90%
set.seed(2) 
aois <- aois %>% 
  mutate(Producer = (rflm[1] + rflm[2] * rf) * 
           runif(n(), min = 0.95, max = 1.05) * 100) %>% 
  select(grp, aois, rf, Accuracy, User, Producer)

```

## Figure 5

Plot of Zones and average accuracy
```{r, eval = FALSE}
# ghana_tilesr %>% group_by(aoi) %>% summarize(aois = mean(aoi)) %>% ungroup %>% 
#   ggplot() + geom_sf(col = "grey70") +
#   geom_sf_text(aes(label = aoi), size = 2) + 
#   geom_sf(data = ghana, fill = "transparent", lwd = 0.3) + 
#   theme_void()

cols <- RColorBrewer::brewer.pal(n = 9, "RdYlGn") %>% #[c(1, 9)] %>% 
  colorRampPalette(colors = .)
# RColorBrewer::display.brewer.all()

# ggsave("manuscript/figures/si_mapping_blocks.png", width = 5, height = 5, 
#        units = "in", dpi = 300)

col_grad <- scale_fill_gradientn(colors = cols(10), limits = c(70, 100), 
                                 breaks = seq(70, 100, 5)) 
p <- map_blocks %>% 
  ggplot() + geom_sf(aes(fill = Accuracy)) + #, col = "grey70") +
  geom_sf_text(aes(label = grp), size = 2) + 
  geom_sf(data = ghana, fill = "transparent", lwd = 0.3) + col_grad + 
  theme_void()
p2 <- map_blocks %>% 
  ggplot() + geom_sf(aes(fill = User)) + #, col = "grey70") +
  geom_sf_text(aes(label = grp), size = 2) + 
  geom_sf(data = ghana, fill = "transparent", lwd = 0.3) + col_grad + 
  theme_void()
p3 <- map_blocks %>% 
  ggplot() + geom_sf(aes(fill = Producer)) + #, col = "grey70") +
  geom_sf_text(aes(label = grp), size = 2) + 
  geom_sf(data = ghana, fill = "transparent", lwd = 0.3) + col_grad + 
  theme_void()

leg <- cowplot::get_legend(p + theme(legend.position = c(0.6, 1)))
gleg <- cowplot::plot_grid(NULL, leg, ncol = 1, align = "h")
gp <- cowplot::plot_grid(p + theme(legend.position = 'none'), 
                         p2 + theme(legend.position = 'none'), 
                         p3 + theme(legend.position = 'none'), nrow = 1, 
                         labels = c("Overall", "User's", "Producer's"), 
                         label_x = 0.0)
gall <- cowplot::plot_grid(gp, gleg, rel_widths = c(1, 0.1), label_x = 0)
# gall

ggsave("manuscript/figures/figure5.png", width = 9, 
       height = 4, units = "in", dpi = 300)

```

## Consensus maps
```{r, eval=FALSE}
library(rmapaccuracy)
library(leaflet)

instance <- "mapper0"
dbase <- "Africa"
host <- paste0(instance, ".crowdmapper.org")
upw <- list("user" = "postgis", "password" = "P0stG1S")
coninfo <- mapper_connect(host)
con <- DBI::dbConnect(RPostgreSQL::PostgreSQL(), host = host,
                      dbname = "Africa", user = upw$user,
                      password = upw$password)

# coninfo <- mapper_connect(host = host)
coninfo$con <- con

common_path <- "~/Dropbox/projects/activelearning/mapper"
common_path <- file.path(common_path, "common")
params <- yaml::yaml.load_file(file.path(common_path, 'config.yaml'))

name <- "GH0431618"#"GH0448854"
sqls <- paste0("select id from master_grid where name='", name, "'")
cid <- DBI::dbGetQuery(con, sqls)[[1]]


user.sql <- paste0("select name, category, worker_id, geom_clean ",
                   "FROM user_maps INNER JOIN categories USING (category)",
                   "INNER JOIN assignment_data USING (assignment_id)",
                   " where name like '",  name, "%' ",
                   "AND categ_group ='field'")

user.polys <- DBI::dbGetQuery(con, gsub(", geom_clean", "", user.sql))
user.polys <- suppressWarnings(st_read(con, query = user.sql))
user.polys <- user.polys %>% filter(st_is(. , "POLYGON"))

# # calling consensus map manually, line by line in script
kmlid <- name
qsite <- FALSE
mode <- "consensus"

# execute consensus script
source(file.path(here::here(), "external/scripts/consensus_labels.R"))
l <- list(user.polys["worker_id"], bayesoutput[[2]], bayesoutput[[1]])
save(l, file = file.path(here::here(), "data/consensus.rda"))

scenes <- tbl(con, "scenes_data") %>% filter(cell_id == cid) %>% 
  dplyr::select(scene_id, cell_id, url, season, tms_url) %>% collect()
# scenes$scene_id

gcs <- "+proj=longlat +datum=WGS84 +no_defs"
name <- tbl(coninfo$con, "master_grid") %>% filter(id == cid) %>%
  dplyr::select(id, name, x, y) %>% collect()
gpoly <- rmapaccuracy::point_to_gridpoly(data.table::data.table(name), 
                                         w = 0.005 / 2, gcs, gcs)

s3url <- scenes %>% filter(season == "GS") %>% pull(url)
planet_path <- file.path("/vsis3", gsub("s3://", "", s3url)) 
planet <- brick(planet_path)

crfeat <- as(extend(extent(as_Spatial(ejura_sites[1, ])), 0.005),
             "SpatialPolygons")
zoomfeat <- as(extend(extent(as_Spatial(ejura_sites[1, ])), 0.002),
               "SpatialPolygons")
proj4string(crfeat) <- proj4string(as_Spatial(user.polys))
proj4string(zoomfeat) <- proj4string(as_Spatial(user.polys))
crfeat_utm <- spTransform(crfeat, crs(planet))
zoomfeat_utm <- spTransform(zoomfeat, crs(planet))
planet_cr <- crop(planet, crfeat_utm)
planet_cr2 <- crop(planet2, crfeat_utm)



# set up display
os <- (scenes %>% filter(season == "OS") %>% filter(row_number() == 1) %>% 
  dplyr::select(tms_url))$tms_url
gs <- (scenes %>% filter(season == "GS") %>% filter(row_number() == 1) %>% 
         dplyr::select(tms_url))$tms_url

m <- leaflet() %>% addTiles() %>% setView(name$x, name$y, zoom = 14) %>% 
  addTiles(os, group = "OS") %>% addTiles(gs, group = "GS") %>% 
  addPolygons(data = gpoly, fill = FALSE, group = "Cell") %>% 
  addLayersControl(overlayGroups = c("Cell", "GS", "OS"),
    options = layersControlOptions(collapsed = FALSE, autoZIndex = FALSE))
m


```

