---
title: "Tightly integrated human and machine intelligence within an active learning approach to cropland mapping"

author: 
  - name: Lyndon Estes
    affiliation: ebd
    email: lestes(at)clarku.edu
    footnote: Corresponding author
    
  # - name: First Coauthor 
  #   affiliation: shortcode

address: 
  - code: ebd
    address: Graduate School of Geography, Clark University, 950 Main Street, Worcester, MA 01610 USA
  - code: shortcode
    address: Full address of First Coauthor

documentclass: elsarticle

output: 
  pdf_document:
    template: elsarticle.latex
    keep_tex: yes
    fig_caption: yes
    toc: false
    
bibliography: ["references.bib"]
csl: ecology.csl

abstract: | 
          Abstract
          
---

<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Example Manuscript}
-->
\linenumbers

```{r knitr_setup, include=FALSE, cache=FALSE}

# library(rmarkdown)
library(knitr)
library(citr)

### Chunk options ###

# Modify at your will #


## Text results
opts_chunk$set(echo = TRUE, warning=TRUE, message=TRUE)

## Code decoration
opts_chunk$set(tidy=TRUE, comment = NA, highlight = TRUE)

## Cache
opts_chunk$set(cache = 2, cache.path = "vignettes/cache/")
opts_chunk$set(cache.extra = rand_seed)

## Plots
opts_chunk$set(fig.path = "vignettes/figures/")
opts_chunk$set(dpi = 300, fig.align = "default")   # may want 'center' sometimes

# Figure format
opts_chunk$set(dev='png')  # e.g. choose among 'pdf', 'png', 'svg'...
# may include specific dev.args as a list... see knitr help

```

```{r citations_setup, include=FALSE, cache=FALSE}

library(knitcitations)
cleanbib()
cite_options(citation_format = "pandoc")

if (file.exists("refs2import.bib"))
  refs <- read.bibtex("refs2import.bib", check=FALSE)
```


# Introduction

- The problem in general 
    - Africa in particular
    - Types of analyses that depend on cropland maps
- Why cropland mapping is hard
    - 3 problems
        - The target itself and its spectral variability and the spectral variability of its background
            - Spectral and spatial resolution of sensors
            - Poses a challenge for classification algorithms, which want both high resolution to be smaller than characteristic field size, but temporal contrast also
    - Training data dependence issues
        - Also interact with image resolution issues
        - Increasingly rely on high amounts of training data
        - Human interpretation error (training data quality)
          - Temporal mismatch with classification feedstock (Lesiv paper)
          - Errors in interpreting these sources of imagery
- Review of who does what to solve the problem (probably integrated with problem statement) 
    - croplands.org
- Our approach that tries to solve these three problems
- Within a framework that tightly integrates tightly training data collection
- And handles large-scale computation
- Segmented boundaries
    
# Methods

- Imagery and image processing methods
- Sample grid
- The system
    - Crowdsourcing platform
          - Training and validation data
          - Accuracy assessment
    - Machine learning
          - Feature engineering
          - ML pipeline Apache Spark
    - Iteration cycle
    - Segmentation

# Results

- Image quality and density
- Labeling results/quality
- Impact of features on accuracy
- Accuracy scores by iteration
- Accuracy by label quality
- Segmentation results 
  - field size class distributions
  - Improvement of accuracy

# Discussion

- Left unquantified is how much training on base maps matters




```{r sessionInfo, cache=FALSE, echo=FALSE, eval=FALSE}
devtools::sessionInfo()
```


# References

<!-- ```{r generate_references, cache=FALSE, include=FALSE, results='hide'} -->
<!-- write.bibtex(file="references.bib",  -->
<!--              append=file.exists("references.bib")) -->

<!-- ``` -->
